Open-source tools in R for landscape ecology

### 2021-04-29 paper/paper.tex
Small typo
A few small changes.

The vector data model consists of two main elements i) geometries (such as points, lines, polygons) and ii) attributes, where each geometry is connected to a row in the attribute table.
In many cases, this data model allows a more realistic representation of landscape features, however, with the higher computational cost \cite{Lovelace2019}.
The \textit{sp} package was the standard for vector data representation for more than ten years \cite{Pebesma2005,Bivand2013}.
As of 2020, more than 500 \textit{R} packages directly depend or imports \textit{sp}.
However, \textit{sp} is not actively developed anymore, and its recommended successor is the \textit{sf} package \cite{Pebesma2018}.
Besides many advantages and strengths of the \textit{sf} package in terms of spatial data handling, it also integrates into the widely used \textit{tidyverse} packages \cite{Wickham2019}.
\textcolor{blue}{The \textit{tidyverse} is a collection of \textit{R} packages developed for almost all major tasks of any data analysis project. 
Because all \textit{tidyverse} packages follow the same data philosophy structures, one strength of the \textit{tidyverse} is its high consistency of usage across its packages \cite{Wickham2019}.}
\textit{sf} builds on the idea of ``simple features,'' a standard used to describe spatial geometries using points, lines (two connected points) and polygons (several connected points), and attributes connected to these geometries \cite{Pebesma2019a}.

@@

To better understand how the landscape ecology community uses \textit{R}, we conducted a short survey using mailing lists and social media to reach the community. \textcolor{blue}{Thus, the survey was not necessarily representative for all skill levels of \textit{R} users and results are most likely biased towards more advanced users.
Also, the survey did not include any personal questions, such as age or country of residence, which might affect the representation of the survey.}.
All raw data and scripts to analyze the data can be found at \url{https://github.com/r-spatialecology/Hesselbarth_et_al_CLER}.

@@

We asked the participants to select which terms describe their research topics the best, and options that were selected by more than 10\% of participants included ``biodiversity,'' followed by ``land use management,'' ``landscape connectivity,'' and ``nature conservation'' (Fig. \ref{fig:fig-survey}a)).

@@

Lastly, when asked how useful \textit{R} is currently for landscape ecology, the vast majority of participants answered with either ``very useful'' or ``useful'' (summarized 90.83\%) and only very few participants evaluated \textit{R} as ``intermediate,'' ``not useful'' or ``not useful at all'' (summarized 9.17\%; Fig. \ref{fig:fig-survey}d)).

>>>>

The vector data model consists of two main elements i) geometries (such as points, lines, polygons) and ii) attributes, where each geometry is connected to a row in the attribute table.
In many cases, this data model allows a more realistic representation of landscape features, however, with the higher computational cost \cite{Lovelace2019}.
The \textit{sp} package was the standard for vector data representation for more than ten years \cite{Pebesma2005,Bivand2013}.
As of 2020, more than 500 \textit{R} packages directly depend or imports \textit{sp}.
However, \textit{sp} is not actively developed anymore, and its recommended successor is the \textit{sf} package \cite{Pebesma2018}.
Besides many advantages and strengths of the \textit{sf} package in terms of spatial data handling, it also integrates into the widely used \textit{tidyverse} packages \cite{Wickham2019}.
\textcolor{blue}{The \textit{tidyverse} is a collection of \textit{R} packages developed for almost all major tasks of any data analysis project. 
Because all \textit{tidyverse} packages follow the same data philosophy structures, one strength of the \textit{tidyverse} is its high consistency of usage across its packages \cite{Wickham2019}.}
\textit{sf} builds on the idea of ``simple features'', a standard used to describe spatial geometries using points, lines (two connected points) and polygons (several connected points), and attributes connected to these geometries \cite{Pebesma2019a}.

@@

To better understand how the landscape ecology community uses \textit{R}, we conducted a short survey using mailing lists and social media to reach the community. \textcolor{blue}{Thus, the survey was not necessarily representative for all skill levels of \textit{R} users and results are most likely biased towards more advanced users.
Also, the survey did not include any personal questions, such as age or country of residence, which might affect the representation of the survey}.
All raw data and scripts to analyze the data can be found at \url{https://github.com/r-spatialecology/Hesselbarth_et_al_CLER}.

@@

We asked the participants to select which terms describe their research topics the best, and options that were selected by more than 10\% of participants included ``biodiversity'', followed by ``land use management'', ``landscape connectivity'', and ``nature conservation'' (Fig. \ref{fig:fig-survey}a).

@@

Lastly, when asked how useful \textit{R} is currently for landscape ecology, the vast majority of participants answered with either ``very useful'' or ``useful'' (summarized 90.83\%) and only very few participants evaluated \textit{R} as ``intermediate'', ``not useful'' or ``not useful at all'' (summarized 9.17\%; Fig. \ref{fig:fig-survey}d).
